D3064R0: OOTA Execution on Real Implementations is Provably Vacuous

### 2024-01-06 ootavacuous.tex
Wordsmith "Inventing Atomic Loads" appendix reactions
Also wordsmith point about "exists" clause being observable behavior.

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

The implementation might also drop the load from \co{y}, whose value
is now unused except by the \co{exists} clause.
However, we use the convention that the \co{exists} clause is observable
behavior.

@@

\begin{enumerate}
\item	Attempts to use real-world constraints to prevent OOTA cycles
	are futile.
	What to do instead?
\item	Implementations should not invent uses for values from
	non-volatile relaxed atomic loads.
	But are there any useful optimizations that invent such uses?
	(One can argue that in all such cases, the loads should instead
	be fused into a single load.)
\item	Listing~\ref{lst:Inventing Atomic Loads}
	looks like it has an OOTA cycle, but there is in fact no
	semantic dependency.
	But then how exactly does one identify a semantic dependency?
\item	What other equally interesting situations might come to light?
\item	Your reaction here!
\end{enumerate}

>>>>

The implementation might also drop the load from \co{y}, whose value
is now unused except by the \co{exists} clause.
However, the \co{exists} clause is considered to be observable behavior,
which means that the load from \co{y} must remain.

@@

\begin{enumerate}
\item	Listing~\ref{lst:Inventing Atomic Loads}
	looks like it has an OOTA cycle, but there is in fact no
	semantic dependency.
\item	Attempts to use real-world constraints to prevent OOTA cycles
	are futile.
	(But see Section~\ref{sec:But What About Non-Volatile Atomics?}.)
\item	Implementations should not invent uses for values from
	non-volatile relaxed atomic loads.
	If it turns out that there are useful optimizations that invent
	such uses, then such optimizations must be applied only with
	careful attention to the as-if rule.
	Some might argue that inventing comparisons between a pair of
	non-volatile relaxed atomic loads from the same object should
	be permitted only if the two loads could be reordered to be
	adjacent to each other.
\item	Any time an impolementation might be tempted to invent uses from
	values from non-volatile relaxed atomic loads, the loads should
	instead be fused into a single load.
	This reaction might be attractive to those who carefully consider
	the pointlessness of keeping two loads that return the same value
	on the one hand or the cache-miss overhead involved should two
	closely spaced loads from the same object return different values
	on the other.
\item	What other interesting situations might come to light?
\end{enumerate}
